\section{Experimental Setup}
\label{sec:experimental.setup}
\subsubsection{Computing System} 
The experiments have been carried out on an Intel Xeon Gold 6248R processor with a Cascade micro-architecture. The processor consists of $24$ cores operating at a base frequency of $3$ GHz.
With $24$ cores and a peak AVX-512 boost frequency of $2.5$ GHz, the processor achieves a theoretical data throughput of ca. $1.92$ double precision Tflops.
We measured a peak performance of $1.78$ double precision Tflops using the likwid performance tool.

We have used \tf{GCC} \tf{v10.2} with the highest optimization level \tf{-O3} and \tf{-march=native}, \tf{-pthread} and \tf{-fopenmp}. 
Loops within for the eighth case have been parallelized using \tf{GCC}'s \tf{OpenMP} \tf{v4.5} implementation.
We have used the \tf{gemv} and \tf{gemm} implementation of the 2024.0 Intel MKL and its own threading library \tf{mkl\_intel\_thread} together with the threading runtime library \tf{libiomp5}.
%todo: tell the number of threads set in openmp and for intel mkl.

If not otherwise mentioned, both tensors $\mubA$ and $\mubC$ are stored according to the first-order linear tensor layout with $\mbpi = (1,\dots,p)$ whereas matrix $\mbB$ has the row-major storage format.
%The benchmark results of each function are the average of 10 runs.
\vspace{-1em}

\subsubsection{Tensor Shapes} 
We have used asymmetrically-shaped and symmetrically-shaped tensors in order to cover many use cases. 
The dimension tuples of both shape types are organized within two three-dimensional arrays with which tensors are initialized.
The dimension array for the first shape type contains $720 = 9\times 8 \times 10$ dimension tuples where the row number is the tensor order ranging from $2$ to $10$. 
For each tensor order, $8$ tensor instances with increasing tensor size is generated.
A special feature of this test set is that the contraction dimension and the leading dimension are disproportionately large. 
The second set consists of $336 = 6\times8\times 7$ dimensions tuples where the tensor order ranges from $2$ to $7$ and has $8$ dimension tuples for each order.
Each tensor dimension within the second set is $2^{12}$, $2^{8}$, $2^{6}$, $2^5$, $2^4$ and $2^3$.
A detailed explanation of the tensor shape setup is given in \cite{bassoy:2019:ttv, bassoy:2018:fast}.